---
title: "Bo Olson"
author: Bo Olson
output: 
  pagedown::html_resume:
    css: ['resume_css.css', 'resume']
knit: pagedown::chrome_print
editor_options: 
  chunk_output_type: console
---

```{r global options, include = FALSE}

knitr::opts_chunk$set (echo = FALSE, warning = FALSE, message = FALSE)

```

```{r libraries used }

library(pagedown)
library(tidyverse)
library(ggridges)
library(wesanderson)
library(viridis)

```

<div class = "densityplot">

```{r fun density plot, fig.height=.75, fig.width=2, fig.align='right'}


wes <- wesanderson::wes_palette("Royal1", type = "continuous", n=12)

data <- data_frame(label = 1, density = c(rnorm(100, mean = 7))) %>% 
          union(data_frame(label = 5, density = c(rnorm(100, mean = 6)))) %>% 
          union(data_frame(label = 6, density = c(rnorm(100, mean = 5)))) %>% 
          union(data_frame(label = 7, density = c(rnorm(100, mean = 4)))) %>% 
          union(data_frame(label = 8, density = c(rnorm(100, mean = 3)))) %>% 
          union(data_frame(label = 9, density = c(rnorm(100, mean = 2)))) 

data %>% ggplot(aes(x =density, y = as.factor(label), fill = factor(label))) + 
                  geom_density_ridges(scale = 2, height =.5, color = "#D5DCBC") + 
                      scale_fill_manual(values = wes)+
                      theme_void()+
                      theme(legend.position = "none",
                            panel.background = element_rect(fill = "#D5DCBC", color = "#D5DCBC"))


```

</div>

::: aside

Contact {#contact}
--------------------------------------

<i class="fa fa-envelope"></i> bo.olson@gmail.com

<i class="fa fa-phone"></i> 847.224.4208

<i class="fa fa-linkedin"></i> <a href="https://linkedin.com/in/OlsonBo">linkedin.com/in/OlsonBo</a>

<!-- hope you like my joke -->

<i class="fa fa-map-marker-alt"></i> <a href="https://www.seattletimes.com/seattle-news/flying-fish-fries-power-for-dozens-of-seattle-city-light-customers/" target="_blank">Seattle, WA</a>

Technical Skills {#skills}
---------------------------------------

```{r skill plot, fig.height=10, fig.width=7}

skill<-c("R", "SQL", "Azure Platform & ETL", "Databricks / Spark", "Python", "Data Visualization (ggplot / PowerBI)")
level<-c(9,10,10,7,5,10)
wes <- wesanderson::wes_palette("Royal1", type = "continuous", n=6)
skills <- data_frame(skill = skill,
                     level = level)

skills %>% ggplot(aes(reorder(skill, level), level)) + 
              geom_col(aes(fill = wes[[2]])) + 
                coord_flip() +
                  scale_fill_manual(values = wes[[2]]) +
                    theme_void() +
                      theme(
                        legend.position = "none",
                        panel.border = element_blank(),
                        panel.background = element_rect(fill = "#D5DCBC", color = "#D5DCBC")
                          ) +
              geom_text(aes(skill, 0, label=skill, group = skill),
                        nudge_y = .25,
                        hjust = 0,
                        family = "Gill Sans",
                        size = 10,
                        color = "white")
```


Interests
---------------------------------------

Avid fly fisher, outdoor wanderer, dog walker, paddler and rower, guitar picker, and poem reader.

<br><br><br>

Disclaimer
---------------------------------------

Built using the awesome <a href="https://github.com/rstudio/pagedown#resume-pagedownhtml_resume">pagedown</a> package

See the source code on my <a href="https://github.com/bo-olson/cv/">github</a>

:::

Main
=======================================

Bo Olson {#title}
---------------------------------------

I'm a full-stack applied data scientist with strong data engineering skills, a creative mind for building enterprise-level ML solutions, and an obession with communicating results beautifully. I'm experienced in driving a data team from descriptive to prescriptive analytics, and bringing stakeholders along for the journey. 

I value empathy in design and communication, and I view analytics and data science as a service meant to improve the daily lives of my peers.


Experience {data-icon=briefcase}
--------------------------------------------------------------------------------

### <i class="fa fa-chart-area"></i> Marketing Analytics Manager 

Microsoft | US Central Marketing Organization

Bellevue, WA

Current - 2016

- Development of enterprise machine learning solutions for US field marketing
- Active work: marketing program recommender algorithms, boosted tree-based targeting models, spend optimization and causal inference models
- Development and maintenance of data pipelines, visual dashboards for hundreds of internal users in sales and marketing


### <i class="fa fa-chart-area"></i> Marketing Program Manager

Yesler

Seattle, WA

2016 - 2014

- Supported Microsoft Enterprise Marketing through reporting platform development
- Development of SSIS, SSAS, PowerBI stack and visual layer


### <i class="fa fa-book-open"></i> Site Merchandiser - Books

Amazon

Seattle, WA

2014 - 2013

- Owned marketing program strategy for a "Big 5" publisher account
- Data analysis, modeling, customer behavior testing
- Merchandising strategy for high-traffic specialty stores & seasonal events

### <i class="fa fa-coffee"></i> Director of Sales

The Tea Spot

Boulder, CO

2013 - 2009

- Managed wholesale sales department 
- Product development, public speaking at industry events

Education {data-icon=university}
--------------------------------------------------------------------------------

### <i class = "fa fa-pen-fancy"></i> Bachelor of English, Creative Writing

University of Colorado

Boulder, CO

2010 - 2006

- Concentration in Poetry
- Editor: Honors Journal (Poetry), Walkabout Arts Journal













