---
title: "Bo Olson"
author: Bo Olson
output: 
  pagedown::html_resume:
    css: ['resume_css.css', 'resume']
#knit: pagedown::chrome_print
editor_options: 
  chunk_output_type: console
---

```{r libraries used, warning=FALSE, echo=FALSE, message=FALSE}

library(pagedown)
library(tidyverse)

```


::: aside

Contact {#contact}
--------------------------------------

<i class="fa fa-envelope"></i> bo.olson@gmail.com

<i class="fa fa-phone"></i> 847.224.4208

<i class="fa fa-linkedin"></i> <a href="https://linkedin.com/in/OlsonBo">linkedin.com/in/OlsonBo</a>

<i class="fa fa-map-marker-alt"></i> Seattle, WA

Technical Skills {#skills}
---------------------------------------

```{r skill plot, warning=FALSE, echo=FALSE, message=FALSE, fig.height=10, fig.width=7}

skill<-c("R", "SQL", "Azure Platform & ETL", "Databricks / Spark", "Python", "Data Visualization (GGplot / PowerBI)")
level<-c(9,10,10,7,5,10)
wes <- wesanderson::wes_palette("Zissou1", type = "continuous", n=6)
skills <- data_frame(skill = skill,
                     level = level)

skills %>% ggplot(aes(reorder(skill, level), level)) + 
              geom_col(aes(fill=skill)) + 
                coord_flip() +
                  scale_fill_manual(values = wes) +
                    theme_void() +
                      theme(
                        legend.position = "none",
                        panel.border = element_blank(),
                        panel.background = element_rect(fill = "#e9edc9", color = "#e9edc9"),
                          ) +
              geom_text(aes(skill, 0, label=skill, group = skill),
                        nudge_y = .25,
                        hjust = 0,
                        family = "Gill Sans",
                        size = 10,
                        color = "white")
```


Interests
---------------------------------------

Avid fly fisher, outdoor wanderer, dog walker, paddler and rower, guitar picker, and poem reader.

<br><br><br>

Disclaimer
---------------------------------------

Built using the awesome <a href="https://github.com/rstudio/pagedown#resume-pagedownhtml_resume">pagedown</a> package

See the source code on my <a href="https://github.com/bo-olson/cv/">github</a>

:::

Main
=======================================

Bo Olson {#title}
---------------------------------------

I'm a full-stack applied data scientist with strong data engineering skills, a creative mind for building enterprise-level ML solutions, and an obession with communicating results beautifully. 

I value empathy in design and communication, and I aspire to connect data-driven insights to human experience.


Experience {data-icon=briefcase}
--------------------------------------------------------------------------------

### <i class="fa fa-chart-area"></i> Marketing Analytics Manager 

Microsoft | US Central Marketing Organization

Bellevue, WA

Current - 2016

- Development of enterprise machine learning solutions for US field marketing
- Active work: marketing program recommender algorithms, boosted tree-based targeting models, spend optimization and causal impact models
- Development and maintenance of data pipelines, visual dashboards for hundreds of internal users in sales and marketing


### <i class="fa fa-chart-area"></i> Marketing Program Manager

Yesler | Client: Microsoft Enterprise Marketing

Seattle, WA

2016 - 2014

- Supported Microsoft Enterprise Marketing through reporting platform development
- Development of SSIS, SSAS, PowerBI stack and visual layer


### <i class="fa fa-book-open"></i> Site Merchandiser - Books

Amazon

Seattle, WA

2014 - 2013

- Owned marketing program strategy for a "Big 5" publisher account
- Data analysis, modeling, customer behavior testing
- Merchandising strategy for high-traffic specialty stores & seasonal events

### <i class="fa fa-coffee"></i> Director of Sales

The Tea Spot

Boulder, CO

2013 - 2009

- Managed wholesale sales department
- Product development, public speaking at industry events

Education {data-icon=university}
--------------------------------------------------------------------------------

### <i class = "fa fa-pen-fancy"></i> Bachelor of English, Creative Writing

University of Colorado

Boulder, CO

2010 - 2006

- Concentration in Poetry
- Editor: Honors Journal (Poetry), Walkabout Arts Journal













